### 2011-01-14 paper/report.tex
First ugly version of report in acm style.  Figures ugly, bibliography commented out (not yet working)
edited methods - hyperNEAT a little...need to figure out details

\url{http://www.youtube.com/watch?v=ODoiOj9DdGg}

@@

\item \emph{Evolutionary Neural Network (HyperNEAT)\cite{clune}}: Near
  the end of term, we hacked together an interface between HyperNEAT
  -- an implementation of a method for evolving neural networks -- and
  the robot, requiring a slightly modified strategy interface.
  Preliminary HyperNEAT runs were promising and resulted in several
  interesting gaits.  Unfortunately, the gaits generated by HyperNEAT
  also tended to stress the robot more than typical gaits had before,
  and the servos would often overheat and malfunction, requiring
  restarts.  We think these issues may be addressed by adding a small
  layer between the HyperNEAT strategy and the robot that disallows
  quickly shifting commanded positions, and we hope to be able to test
  these methods further once this filter is in place.

>>>>

%\url{http://www.youtube.com/watch?v=ODoiOj9DdGg}
\texttt{http://www.youtube.com/watch?v=ODoiOj9DdGg}

@@

\item \emph{Evolutionary Neural Network (HyperNEAT)\cite{clune}}: We 
  put together an interface between HyperNEAT
  -- an implementation of a method for evolving neural networks -- and
  the robot, requiring a slightly modified strategy interface.

  % Preliminary HyperNEAT runs were promising and resulted in several
  % interesting gaits.

  % Unfortunately, the gaits generated by HyperNEAT
  % also tended to stress the robot more than typical gaits had before,
  % and the servos would often overheat and malfunction, requiring
  % restarts.  We think these issues may be addressed by adding a small
  % layer between the HyperNEAT strategy and the robot that disallows
  % quickly shifting commanded positions, and we hope to be able to test
  % these methods further once this filter is in place.
